Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-27 paper.tex
make paragraph flow more better

The $L$ cast representation is defined in \figref{fig:L-instance-LazyD}.
Casts in $L$ are lists of steps ($s$), where every step is like a cast in 
\ineffCEKD. The operators $id$ and $seq$ are the empty list and list appending 
respectively. And $applyCast$ applies steps from left to right. Steps are 
confined by its type rule such that its source and target are different. This 
restriction is necessary to show $cast(T,l,T) = id(T)$.

>>>>

The $L$ cast representation is defined in \figref{fig:L-instance-LazyD}.
Casts in $L$ are lists of steps ($s$), where every step is like a cast in 
\ineffCEKD. The function $applyCast$ applies steps from left to right. Steps are 
restricted by its typing rule such that its source and target are different. This 
restriction is necessary to show $cast(T,l,T) = id(T)$. With this representation
of casts, the operators $id$ and $seq$ are the empty list of steps and list
append on casts respectively.
